ZPY: Open Source Synthetic Data for Computer Vision

### 2021-07-07 docs/paper/paper.tex
Fixed citations, better image for software3

\usepackage[backend=biber, style=numeric]{biblatex}
\addbibresource{references.bib}
% \RequirePackage[backend=biber,
% style=apa,
% citestyle=authoryear
% ]{biblatex}
% \usepackage[square,numbers]{natbib}

@@

Assets are digital representations of a 3D object. One type of asset is a mesh: a connected graph of 3D points also called vertices, which define the surface of an object. Edges interconnect vertices, and a closed loop of vertices creates a polygon known as a face. The engineering and manufacturing world creates meshes using computer-aided design (CAD) software such as AutoCAD \cite{autocad}, Solidworks \cite{solidworks}, Onshape \cite{onshape}, and Rhino \cite{rhino}. The entertainment industry creates meshes using modeling software such as Maya \cite{maya}, 3DSMax \cite{3dsmax}, and Cinema4D \cite{cinema4d}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{software3.png}
	\caption{Software 3.0: the developer transitions from writing explicit algorithms to creating and curating datasets which are used to train machine learning models.}
	\label{fig:fig2}
\end{figure}

@@

% \bibliographystyle{abbrvnat}
% \bibliography{references}
\printbibliography

>>>>

\usepackage[square,numbers]{natbib}

@@

Assets are digital representations of a 3D object. One type of asset is a mesh: a connected graph of 3D points also called vertices, which define the surface of an object. Edges interconnect vertices, and a closed loop of vertices creates a polygon known as a face.

The engineering and manufacturing world creates meshes using computer-aided design (CAD) software such as AutoCAD \cite{autocad}, Solidworks \cite{solidworks}, Onshape \cite{onshape}, and Rhino \cite{rhino}. The entertainment industry creates meshes using modeling software such as Maya \cite{maya}, 3DSMax \cite{3dsmax}, and Cinema4D \cite{cinema4d}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{software3.png}
	\caption{The developer transitions from writing explicit rule-based algorithms (\emph{Software 2.0}) to creating and curating datasets and labels which are used to train machine learning algorithms (\emph{Software 3.0}).}
	\label{fig:fig2}
\end{figure}

@@

\bibliographystyle{abbrvnat}
\bibliography{references}
